---
title: "Using Tidyquant and Plotly: A Simple Introduction"
output: html_notebook
---

## Installation
```{r include=FALSE}
library(tidyquant)
library(plotly)
```

To have access to the quandl data, it is better to declare my API address, for example:

```{r eval=FALSE}
quandl_api_key("enter-your-api-key-here")
```

## Import data (in a tibble form)
Import two time series in levels:
```{r}
dat01 <- c("FRED/CTFPPPJPA669NRUG", 
            "FRED/CTFPPPBOA669NRUG") %>%
    tq_get(get          = "quandl",
           from         = "1950-01-01",
           to           = "2014-01-01",
           collapse     = "annual")       
```

Import two time series in growth rates:
```{r}
dat02 <- c("FRED/CTFPPPJPA669NRUG", 
            "FRED/CTFPPPBOA669NRUG") %>%
    tq_get(get          = "quandl",
           from         = "1950-01-01",
           to           = "2014-01-01",
           transform    = "rdiff",
           collapse     = "annual")    
```



## Wrangle the data

Recode the name of the countries and create a factor variable:
```{r}
dat01$symbol_rec <- recode(dat01$symbol,
               "FRED/CTFPPPJPA669NRUG" = "Japan",
               "FRED/CTFPPPBOA669NRUG" = "Bolivia")
dat01$symbol_rec <- factor(dat01$symbol_rec)
```

```{r}
dat02$symbol_rec <- recode(dat02$symbol,
               "FRED/CTFPPPJPA669NRUG" = "Japan",
               "FRED/CTFPPPBOA669NRUG" = "Bolivia")
dat02$symbol_rec <- factor(dat02$symbol_rec)
```

## Visualize levels

```{r}
fig01 <- dat01 %>%
  ggplot(aes(x = date,
             y = value,
             color = symbol_rec)) +
  geom_line()
```

Here is an interactive visualization via `Plotly`

```{r}
ggplotly(fig01)
```

## Visualize growth rates

```{r}
fig02 <- dat02 %>%
  ggplot(aes(x = date,
             y = value,
             color = symbol_rec)) +
  geom_line()
```

Here is an interactive visualization via `Plotly`

```{r}
ggplotly(fig02)
```

## Rendering of this documents
The interactive html version of this document can be accessed from: <https://rawgit.com/ds777/tidyquant-and-html-widgets/master/tidyquant-and-html-widgets.nb.html>

## Additional references
- <https://business-science.github.io/tidyquant/articles/TQ01-core-functions-in-tidyquant.html>
- <https://plot.ly/ggplot2/getting-started/>